{\bf {\Large Title....}}

### 2016-07-30 ident_manu.Rnw
sensalltile to supplementary

Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in \Sexpr{nrow(sens_ests_cat)} of 250 parameters (\Sexpr{round(100 * nrow(sens_ests_cat)/250, 0)}\% of total) in FishTank. Within each parameter category, \ac{do} was sensitive to \Sexpr{bycat$Optics} parameters for optics (\Sexpr{lncats$Optics} of all optic parameters, \cref{tab:optsens}), \Sexpr{bycat$`Organic Matter`} for organic matter (\Sexpr{lncats$`Organic Matter`}, \cref{tab:omsens}), \Sexpr{bycat$Phytoplankton} for phytoplankton (\Sexpr{lncats$Phytoplankton}, \cref{tab:phytosens}), \Sexpr{bycat$Temperature} for temperature (\Sexpr{lncats$Temperature}, \cref{tab:tempsens}), and \Sexpr{bycat$Zooplankton} for zooplankton (\Sexpr{lncats$Zooplankton}, \cref{tab:zoopsens}). Although \ac{do} had the greatest sensitivity to parameters in the zooplankton category (as percentage of total), the relative effects varied. Among all parameters, sensitivity values ranged from $L1 = $ \Sexpr{sensrng$error[1]} for \Sexpr{sensrng$Parameter[1]} (\Sexpr{tolower(sensrng$Category[1])}) to \Sexpr{sensrng$error[2]} for \Sexpr{sensrng$Parameter[2]} (\Sexpr{tolower(sensrng$Category[2])}), whereas average sensitivity among all parameters was $L1 = $ \Sexpr{sensave}.  Within categories, sensitivity ranged from \Sexpr{sensrngcat$Optics$error[1]} (\Sexpr{sensrngcat$Optics$Parameter[1]}) to \Sexpr{sensrngcat$Optics$error[2]} (\Sexpr{sensrngcat$Optics$Parameter[2]}) for optics, \Sexpr{sensrngcat$`Organic Matter`$error[1]} (\Sexpr{sensrngcat$`Organic Matter`$Parameter[1]}) to \Sexpr{sensrngcat$`Organic Matter`$error[2]} (\Sexpr{sensrngcat$`Organic Matter`$Parameter[2]}) for organic matter, \Sexpr{sensrngcat$Phytoplankton$error[1]} (\Sexpr{sensrngcat$Phytoplankton$Parameter[1]}) to \Sexpr{sensrngcat$Phytoplankton$error[2]} (\Sexpr{sensrngcat$Phytoplankton$Parameter[2]}) for phytopankton, \Sexpr{sensrngcat$Temperature$error[1]} (\Sexpr{sensrngcat$Temperature$Parameter[1]}) to \Sexpr{sensrngcat$Temperature$error[2]} (\Sexpr{sensrngcat$Temperature$Parameter[2]}) for temperature, and \Sexpr{sensrngcat$Zooplankton$error[1]} (\Sexpr{sensrngcat$Zooplankton$Parameter[1]}) to \Sexpr{sensrngcat$Zooplankton$error[2]} (\Sexpr{sensrngcat$Zooplankton$Parameter[2]}) for zooplankton (\cref{fig:sensplo}, bottom).  Average sensitivity values in each category were $L1 = $ \Sexpr{sensave_cat$Optics} for optics, \Sexpr{sensave_cat$`Organic Matter`} for organic matter, \Sexpr{sensave_cat$Phytoplankton} for phytoplankton, \Sexpr{sensave_cat$Temperature} for temperature, and \Sexpr{sensave_cat$Zooplankton} for zooplankton.  Within the six phytoplankton groups, \ac{do} was sensitive to the same parameters within each group although the sensitivity magnitudes varied. Average sensitivity across parameters in each phytoplankton groups showed that \ac{do} was most sensitive to the first and third phytoplankton groups (average $L1 = $ \Sexpr{phytogrps[1, 2]}, \Sexpr{phytogrps[2, 2]}), whereas sensitivity to parameters in the remaining groups was much lower (all with average $L1 < 1$). Sensitivity of \ac{do} did not vary considerably between parameters in the two zooplankton groups (average $L1 = $ \Sexpr{zoopgrps[1, 2]}, \Sexpr{zoopgrps[2, 2]} for groups one and two).

@@

We showed only small subsets are identifiable, similar conclusions have been described by citations in \citep{Wagener01}, p. 14 for models that follow traditional calibration schemes (e.g., objective function minimization).

@@

@@

ggplot(toplo, aes(x = Selected, y = coll)) + 
  geom_line() + 
  geom_point(aes(fill = Category), shape = 21, size = 4) +
  geom_hline(yintercept = 15, linetype = 'longdash', colour = 'darkgrey') + 
  geom_hline(yintercept = 10, linetype = 'dotted', colour = 'darkgrey') + 
  facet_wrap(~L1, scales= 'free', ncol = 4) + 
  scale_y_continuous('Identifiability') + 
  scale_x_continuous(
    'Parameters selected by sensitivity',
    breaks = toplo$Selected
    ) + 
  cols +
  pthm +
  theme(legend.position = c(0.9, 0.2))
@

\clearpage
%%%%%%
% tables

% zooplankton sensitivity
<<zoopsens, eval = T, cache = F>>=
senstab2('Zooplankton', 'zoopsens')
@

>>>>

Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in \Sexpr{nrow(sens_ests_cat)} of 250 parameters (\Sexpr{round(100 * nrow(sens_ests_cat)/250, 0)}\% of total) in FishTank (see \cref{fig:sensalltile} for other state variables). Within each parameter category, \ac{do} was sensitive to \Sexpr{bycat$Optics} parameters for optics (\Sexpr{lncats$Optics} of all optic parameters, \cref{tab:optsens}), \Sexpr{bycat$`Organic Matter`} for organic matter (\Sexpr{lncats$`Organic Matter`}, \cref{tab:omsens}), \Sexpr{bycat$Phytoplankton} for phytoplankton (\Sexpr{lncats$Phytoplankton}, \cref{tab:phytosens}), \Sexpr{bycat$Temperature} for temperature (\Sexpr{lncats$Temperature}, \cref{tab:tempsens}), and \Sexpr{bycat$Zooplankton} for zooplankton (\Sexpr{lncats$Zooplankton}, \cref{tab:zoopsens}). Although \ac{do} had the greatest sensitivity to parameters in the zooplankton category (as percentage of total), the relative effects varied. Among all parameters, sensitivity values ranged from $L1 = $ \Sexpr{sensrng$error[1]} for \Sexpr{sensrng$Parameter[1]} (\Sexpr{tolower(sensrng$Category[1])}) to \Sexpr{sensrng$error[2]} for \Sexpr{sensrng$Parameter[2]} (\Sexpr{tolower(sensrng$Category[2])}), whereas average sensitivity among all parameters was $L1 = $ \Sexpr{sensave}.  Within categories, sensitivity ranged from \Sexpr{sensrngcat$Optics$error[1]} (\Sexpr{sensrngcat$Optics$Parameter[1]}) to \Sexpr{sensrngcat$Optics$error[2]} (\Sexpr{sensrngcat$Optics$Parameter[2]}) for optics, \Sexpr{sensrngcat$`Organic Matter`$error[1]} (\Sexpr{sensrngcat$`Organic Matter`$Parameter[1]}) to \Sexpr{sensrngcat$`Organic Matter`$error[2]} (\Sexpr{sensrngcat$`Organic Matter`$Parameter[2]}) for organic matter, \Sexpr{sensrngcat$Phytoplankton$error[1]} (\Sexpr{sensrngcat$Phytoplankton$Parameter[1]}) to \Sexpr{sensrngcat$Phytoplankton$error[2]} (\Sexpr{sensrngcat$Phytoplankton$Parameter[2]}) for phytopankton, \Sexpr{sensrngcat$Temperature$error[1]} (\Sexpr{sensrngcat$Temperature$Parameter[1]}) to \Sexpr{sensrngcat$Temperature$error[2]} (\Sexpr{sensrngcat$Temperature$Parameter[2]}) for temperature, and \Sexpr{sensrngcat$Zooplankton$error[1]} (\Sexpr{sensrngcat$Zooplankton$Parameter[1]}) to \Sexpr{sensrngcat$Zooplankton$error[2]} (\Sexpr{sensrngcat$Zooplankton$Parameter[2]}) for zooplankton (\cref{fig:sensplo}, bottom).  Average sensitivity values in each category were $L1 = $ \Sexpr{sensave_cat$Optics} for optics, \Sexpr{sensave_cat$`Organic Matter`} for organic matter, \Sexpr{sensave_cat$Phytoplankton} for phytoplankton, \Sexpr{sensave_cat$Temperature} for temperature, and \Sexpr{sensave_cat$Zooplankton} for zooplankton.  Within the six phytoplankton groups, \ac{do} was sensitive to the same parameters within each group although the sensitivity magnitudes varied. Average sensitivity across parameters in each phytoplankton groups showed that \ac{do} was most sensitive to the first and third phytoplankton groups (average $L1 = $ \Sexpr{phytogrps[1, 2]}, \Sexpr{phytogrps[2, 2]}), whereas sensitivity to parameters in the remaining groups was much lower (all with average $L1 < 1$). Sensitivity of \ac{do} did not vary considerably between parameters in the two zooplankton groups (average $L1 = $ \Sexpr{zoopgrps[1, 2]}, \Sexpr{zoopgrps[2, 2]} for groups one and two).

@@

% back of envelop calcs for number of relevant parms, all state variables
<<echo = F>>=

@
We showed only small subsets are identifiable, similar conclusions have been described by citations in \citep{Wagener01}, p. 14 for models that follow traditional calibration schemes (e.g., objective function minimization).

@@

%%%%%%
% tables

% zooplankton sensitivity
<<zoopsens, eval = T, cache = F>>=
senstab2('Zooplankton', 'zoopsens')
@
\clearpage

@@

ggplot(toplo, aes(x = Selected, y = coll)) + 
  geom_line() + 
  geom_point(aes(fill = Category), shape = 21, size = 4) +
  geom_hline(yintercept = 15, linetype = 'longdash', colour = 'darkgrey') + 
  geom_hline(yintercept = 10, linetype = 'dotted', colour = 'darkgrey') + 
  facet_wrap(~L1, scales= 'free', ncol = 4) + 
  scale_y_continuous('Identifiability') + 
  scale_x_continuous(
    'Parameters selected by sensitivity',
    breaks = toplo$Selected
    ) + 
  cols +
  pthm +
  theme(legend.position = c(0.9, 0.2))
@
\clearpage

% supplementary material
\beginsupplement

<<sensalltile, echo = F, fig.height = 9, fig.width = 9, out.width = '\\textwidth', fig.cap = 'Sensitivity values (L1, \\cref{l1}) for local analyses of all state variables.  Values are truncated by the 5\\textsuperscript{th} and 95\\textsuperscript{th} sensitivity values between all parameters for visual appearance. Parameters are grouped by category (plot strips).  Phytoplankton and zooplankton categories are further separated into one through six, and one and two groups (p1 - p6, z1 - z2), respectively.'>>=
data(sens_ests_cat_all)

tmp <- reshape2::melt(sens_ests_cat_all, id.var = c('Parameter', 'error', 'Category'))

lims <- with(tmp, quantile(error, c(0.05, 0.95))) %>% 
  as.numeric

stts_lev <- c('Chla_mg_tot', 'irradiance', 'NH4', 'NO3', 'O2', 'OM1', 'OM2', 'PO4')
stts_lab <- c('Chlorophyll', 'Irradiance', 'Ammonium', 'Nitrate', 'Dissolved Oxygen', 'OM1', 'OM2', 'Phosphate')

toplo <- filter(tmp, error < lims[2] & error > lims[1]) %>% 
  mutate(
    L1 = factor(L1, levels = stts_lev, labels = stts_lab)
  ) %>% 
  rename(Sensitivity = error)

toplo1 <- filter(toplo, !Category %in% c('Phytoplankton', 'Zooplankton')) %>% 
  mutate(Parameter = as.character(par_txt(Parameter, frm = 'exp')))
toplo2 <- filter(toplo, Category %in% c('Phytoplankton')) %>% 
  mutate(
    grp = gsub('^.*_([1-6])$', 'p\\1', Parameter), 
    Parameter = as.character(par_txt(Parameter, frm = 'exp'))
  )
toplo3 <- filter(toplo, Category %in% c('Zooplankton')) %>% 
  mutate(
    grp = gsub('^.*_([1-2])$', 'z\\1', Parameter), 
    Parameter = as.character(par_txt(Parameter, frm = 'exp'))
  )

pbase <- theme(
  panel.grid.major = element_blank(), 
  panel.grid.minor = element_blank(), 
  axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 6), 
  axis.text.y = element_text(size =8),
  axis.title.y = element_blank(), 
  axis.title.x = element_blank(),
  legend.position = 'none', 
  plot.margin = grid::unit(c(2, 2, 2, 2), 'pt')
  )

p1 <- ggplot(toplo1, aes(x = Parameter, y = L1, fill = Sensitivity)) + 
  geom_tile() + 
  pbase +
  scale_x_discrete(expand = c(0, 0),
    breaks = toplo1$Parameter, 
    labels = parse(text = toplo1$Parameter)
    ) + 
  scale_y_discrete(expand = c(0, 0)) +
  scale_fill_distiller(palette = "Spectral", limits = lims) + 
  facet_grid(~Category, scales = 'free')
p2 <- ggplot(toplo2, aes(x = Parameter, y = L1, fill = Sensitivity)) + 
  geom_tile() + 
  pbase +
  scale_x_discrete(expand = c(0, 0), 
    breaks = toplo2$Parameter, 
    labels = parse(text = toplo2$Parameter)
    ) + 
  scale_y_discrete(expand = c(0, 0)) +
  scale_fill_distiller(palette = "Spectral", limits = lims) + 
  facet_grid(~grp, scales = 'free') + 
  ggtitle('Phytoplankton')
p3 <- ggplot(toplo3, aes(x = Parameter, y = L1, fill = Sensitivity)) + 
  geom_tile() + 
  pbase +
  scale_x_discrete(expand = c(0, 0), 
    breaks = toplo3$Parameter, 
    labels = parse(text = toplo3$Parameter)
    ) + 
  scale_y_discrete(expand = c(0, 0)) + 
  scale_fill_distiller(palette = "Spectral", limits = lims) + 
  facet_grid(~grp, scales = 'free') + 
  ggtitle('Zooplankton') + 
  theme(legend.position = 'top')
pleg <- g_legend(p3)
p3 <- p3 + theme(legend.position = 'none')

grid.arrange(
  pleg, p1, p2, p3, ncol = 1, 
  heights = c(0.2, 1, 0.85, 1),
  bottom = 'Parameter', 
  left = 'State variable'
)
@

### 2016-07-30 ident_manu.tex
sens_ests_all and sens_ests_cat_all to data
sensalltile to supplementary

\begin{singlespace}
\title{{\bf {\Large Title....}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^1$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:lehrter.john@epa.gov}{lehrter.john@epa.gov}}}
  \vspace{1in} 
  \\ Version Date:   Mon Jul 11 11:13:58 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

\subsection{Identifiability to evaluate structural uncertainty}

@@

Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in 140 of 250 parameters (56\% of total) in FishTank. Within each parameter category, \ac{do} was sensitive to four parameters for optics (36\% of all optic parameters, \cref{tab:optsens}), seven for organic matter (24\%, \cref{tab:omsens}), 103 for phytoplankton (66\%, \cref{tab:phytosens}), seven for temperature (22\%, \cref{tab:tempsens}), and 19 for zooplankton (86\%, \cref{tab:zoopsens}). Although \ac{do} had the greatest sensitivity to parameters in the zooplankton category (as percentage of total), the relative effects varied. Among all parameters, sensitivity values ranged from $L1 = $ $3.18\times 10^{-6}$ for \textit{Kcdom} (optics) to $328.35$ for \textit{Qc$_{p1}$} (phytoplankton), whereas average sensitivity among all parameters was $L1 = $ $4.52$.  Within categories, sensitivity ranged from $3.18\times 10^{-6}$ (\textit{Kcdom}) to $1.64$ (\textit{astar490}) for optics, $0.01$ (\textit{KGcdom}) to $2.11$ (\textit{k11}) for organic matter, $1\times 10^{-5}$ (\textit{Ksi$_{p1}$}) to $328.35$ (\textit{Qc$_{p1}$}) for phytopankton, $0.12$ (\textit{Tref(nospA+nospZ)$_{p1}$}) to $2.9$ (\textit{Tref(nospA+nospZ)$_{p4}$}) for temperature, and $0$ (\textit{ZQp$_{z1}$}) to $0.82$ (\textit{ZKa$_{z1}$}) for zooplankton (\cref{fig:sensplo}, bottom).  Average sensitivity values in each category were $L1 = $ $0.42$ for optics, $1.24$ for organic matter, $5.96$ for phytoplankton, $0.55$ for temperature, and $0.27$ for zooplankton.  Within the six phytoplankton groups, \ac{do} was sensitive to the same parameters within each group although the sensitivity magnitudes varied. Average sensitivity across parameters in each phytoplankton groups showed that \ac{do} was most sensitive to the first and third phytoplankton groups (average $L1 = $ $19.71$, $14.56$), whereas sensitivity to parameters in the remaining groups was much lower (all with average $L1 < 1$). Sensitivity of \ac{do} did not vary considerably between parameters in the two zooplankton groups (average $L1 = $ $0.31$, $0.23$ for groups one and two).

@@

@@

@@

\clearpage
%%%%%%
% tables

>>>>

\begin{singlespace}
\title{{\bf {\Large Title....}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^1$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:lehrter.john@epa.gov}{lehrter.john@epa.gov}}}
  \vspace{1in} 
  \\ Version Date:   Fri Jul 29 17:27:00 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

\subsection{Identifiability and structural uncertainty}

@@

Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in 140 of 250 parameters (56\% of total) in FishTank (see \cref{fig:sensalltile} for other state variables). Within each parameter category, \ac{do} was sensitive to four parameters for optics (36\% of all optic parameters, \cref{tab:optsens}), seven for organic matter (24\%, \cref{tab:omsens}), 103 for phytoplankton (66\%, \cref{tab:phytosens}), seven for temperature (22\%, \cref{tab:tempsens}), and 19 for zooplankton (86\%, \cref{tab:zoopsens}). Although \ac{do} had the greatest sensitivity to parameters in the zooplankton category (as percentage of total), the relative effects varied. Among all parameters, sensitivity values ranged from $L1 = $ $3.18\times 10^{-6}$ for \textit{Kcdom} (optics) to $328.35$ for \textit{Qc$_{p1}$} (phytoplankton), whereas average sensitivity among all parameters was $L1 = $ $4.52$.  Within categories, sensitivity ranged from $3.18\times 10^{-6}$ (\textit{Kcdom}) to $1.64$ (\textit{astar490}) for optics, $0.01$ (\textit{KGcdom}) to $2.11$ (\textit{k11}) for organic matter, $1\times 10^{-5}$ (\textit{Ksi$_{p1}$}) to $328.35$ (\textit{Qc$_{p1}$}) for phytopankton, $0.12$ (\textit{Tref(nospA+nospZ)$_{p1}$}) to $2.9$ (\textit{Tref(nospA+nospZ)$_{p4}$}) for temperature, and $0$ (\textit{ZQp$_{z1}$}) to $0.82$ (\textit{ZKa$_{z1}$}) for zooplankton (\cref{fig:sensplo}, bottom).  Average sensitivity values in each category were $L1 = $ $0.42$ for optics, $1.24$ for organic matter, $5.96$ for phytoplankton, $0.55$ for temperature, and $0.27$ for zooplankton.  Within the six phytoplankton groups, \ac{do} was sensitive to the same parameters within each group although the sensitivity magnitudes varied. Average sensitivity across parameters in each phytoplankton groups showed that \ac{do} was most sensitive to the first and third phytoplankton groups (average $L1 = $ $19.71$, $14.56$), whereas sensitivity to parameters in the remaining groups was much lower (all with average $L1 < 1$). Sensitivity of \ac{do} did not vary considerably between parameters in the two zooplankton groups (average $L1 = $ $0.31$, $0.23$ for groups one and two).

@@

% back of envelop calcs for number of relevant parms, all state variables

@@

%%%%%%
% tables

\clearpage

@@

\clearpage

% supplementary material
\beginsupplement

\begin{figure}[!ht]

{\centering \includegraphics[width=\textwidth]{figs/sensalltile-1}

\caption{Sensitivity values (L1, \cref{l1}) for local analyses of all state variables.  Values are truncated by the 5\textsuperscript{th} and 95\textsuperscript{th} sensitivity values between all parameters for visual appearance. Parameters are grouped by category (plot strips).  Phytoplankton and zooplankton categories are further separated into one through six, and one and two groups (p1 - p6, z1 - z2), respectively.}\label{fig:sensalltile}
\end{figure}
